R Python, and Ruby clients for GBIF species occurrence data

### 2017-09-07 manuscript.tex
remake pdf

Dataset metrics are another useful way of figuring out what datasets you
may want to use. One drawback is that these metrics data are only
available for datasets of type \emph{checklist}, but there are quite a
lot of them (21502).

@@

Both R and Python are commonly used in science, and can be used for
similar tasks. Python, however, is a more general programming lanugae,
and can be used in more contexts than R can be used in.

The \texttt{rgbif} and \texttt{pygbif} clients can do a lot of the same
tasks. We envision \texttt{rgbif} as being more common in workflows of
academics asking research questions, whereas \texttt{pygbif} can do that
as well, but may be more easily used in a website.

The R client \texttt{rgbif} has much more development time than
\texttt{pygbif}, but through time \texttt{pygbif} will become equally
mature.

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{library}\NormalTok{(}\StringTok{"rgbif"}\NormalTok{)}
\KeywordTok{library}\NormalTok{(}\StringTok{"dismo"}\NormalTok{)}
\KeywordTok{library}\NormalTok{(}\StringTok{"maptools"}\NormalTok{)}
\KeywordTok{library}\NormalTok{(}\StringTok{"dplyr"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

>>>>

Dataset metrics are another useful way of figuring out what datasets you
may want to use. One drawback is that these metrics data are only
available for datasets of type \emph{checklist}, but there are quite a
lot of them (21522).

@@

Both R and Python are commonly used in science, and can be used for
similar tasks. Python, however, is a more general programming lanugae,
and can be used in more contexts than R can be used in. Ruby is used
very little in science; but, like Python, Ruby is very widely used as a
general purpose programming language, with heavy use in web development
and web services.

The three clients can do a lot of the same tasks. We envision
\texttt{rgbif} being more common in workflows of academics asking
research questions, whereas \texttt{pygbif} and \texttt{gbifrb} can do
that as well, but may be more easily used in a website.

The R client \texttt{rgbif} has had much more development time than
\texttt{pygbif} and \texttt{gbifrb}, but with time \texttt{pygbif} and
\texttt{gbifrb} will become equally mature.

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{library}\NormalTok{(}\StringTok{"sp"}\NormalTok{)}
\KeywordTok{library}\NormalTok{(}\StringTok{"rgbif"}\NormalTok{)}
\KeywordTok{library}\NormalTok{(}\StringTok{"dismo"}\NormalTok{)}
\KeywordTok{library}\NormalTok{(}\StringTok{"maptools"}\NormalTok{)}
\KeywordTok{library}\NormalTok{(}\StringTok{"dplyr"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}
